Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-06 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
reviewer 2: (D.4) Blackburn reference added.

From an axiomatic point of view, modal logics differ with respect to which additional axiom schemas they admit. Some common axiom schemas of relevance to the ontological argument are T ($\nec A \imp A$), B ($A \imp \nec \pos A$), 4 ($\nec A \imp \nec \nec A $) and 5 ($\pos A \imp \nec \pos A$). From a semantic point of view, these axioms correspond to geometric frame conditions that must be satisfied by the accessibility relation in Kripke models (See for example \citep{fitting2}): T corresponds to reflexivity, B corresponds to symmetry, 4 corresponds to transitivity and 5 corresponds to euclidianity. In the models of logic {\bf S5}, all these axioms are satisfied; in the models of logic {\bf KB}, K and B are satisfied; and in the models of logic {\bf B}, K, T and B are satisfied.

@@

@@

% @inproceedings{IJCAI2016,
%   author = {Benzmüller, C. and Woltzenlogel Paleo, B.},
%   title  = {The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics},
%   booktitle = {International Joint Conference on Artificial Intelligence - IJCAI},
%   keywords ={HOML,Bruno,COREA*},
%   year = {2016}
% }

% @article{AndersonHajekControversy,
%     author = {Benzmüller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-Hájek Ontological Controversy},
%     journal = {Logica Universalis},
%     publisher = {Springer},
%     issn = {1661-8297},
%     volume = {10},
%     year = {2016},
%     keywords = {Bruno,HOML},
%     pages = {1--10},
%     note = {\emph{Accepted for publication on the 28th of February 2016}}
% }

% @inproceedings{WorldCongressLogicAndReligion,
%     author = {Benzmüller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-Hájek Ontological Controversy},
%     booktitle = {1st World Congress on Logic and Religion},
%     year = {2015},
%     keywords = {Bruno,Abstract,HOML},
%     pages = {49--50}
% }

% @inproceeding{WADT,
%    author = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and Gödel's God},
%    booktitle = {Recent Trends in Algebraic Development Techniques},
%    year = {2014},
%    crossref = {ADT},
%    keywords = {Bruno,Invited,HOML},
%    note = {\textbf{[Invited]} }
% }

% @inproceedings{SpiritualQuest,
%   author    = {Christoph Benzmüller and Bruno Woltzenlogel Paleo},
%   title     = {Experiments in Computational Metaphysics: Gödel's Proof of God's Existence},
%   booktitle = {Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November)},
%   year      = {2015},
%   crossref  = {SpiritualQuest},
%   volume    = {9},
%   keywords  = {Bruno,Invited,HOML},
%   note = {\textbf{[Invited]} },
%   pages = {23--40}
% }

@@

% @inproceedings{SquareOfOpposition,
%    author = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {Formalization and Automated Verification of Gödel's Proof of God's Existence},
%    booktitle = {4th World Congress on the Square of Opposition},
%    year = {2014},
%    keywords = {Bruno,Abstract,HOML},
%    pages = {24--25}
% }

% @inworkshopinvited{WADTPreProceedings,
%    author = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and Gödel's God},
%    booktitle = {22nd International Workshop on Algebraic Development Techniques},
%    year = {2014},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {8--9},
%    url = {http://wadt2014.cs.ovgu.de/pre-proceedings.pdf}
% }

% @article{ModalCollapse,
%    author = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {The Modal Collapse as a Collapse of the Modal Square of Opposition},
%    journal = {Studies in Universal Logic},
%    publisher = {Springer},
%    issn = {2297-0282},
%    year = {2016},
%    keywords = {Bruno,HOML},
%    pages   =  {1--7},
%    note    = {\emph{Submitted in November 2014. Accepted for publication on the 28th of February 2016}}
% }

% @article{IsabelleGod,
%   author    = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%   title     = {G{\"{o}}del's God in Isabelle/HOL},
%   journal   = {Archive of Formal Proofs},
%   year      = {2013},
%   volume    = {},
%   keywords  = {Bruno,DBLP,HOML},
%   url       = {http://afp.sourceforge.net/entries/GoedelGod.shtml},
%   timestamp = {Wed, 15 Oct 2014 15:14:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/journals/afp/Benzmueller13},
%   bibsource = {dblp computer science bibliography, http://dblp.org}
% }

% @inworkshopinvited{IWIL,
%    author = {Benzmüller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {Gödel's God on the Computer},
%    booktitle = {10th International Workshop on the Implementation of Logics},
%    year = {2013},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {1--2}
% }

% @article{AustrianComputerSociety,
%    author = {Woltzenlogel Paleo, Bruno},
%    title  = {Automated Verification and Reconstruction of Gödel's Proof of God's Existence},
%    journal = {Journal of the Austrian Computer Society},
%    year = {2013},
%    keywords = {Bruno,Invited,S,HOML},
%    pages    = {4--6}
% }

>>>>

From an axiomatic point of view, modal logics differ with respect to which additional axiom schemas they admit. Some common axiom schemas of relevance to the ontological argument are T ($\nec A \imp A$), B ($A \imp \nec \pos A$), 4 ($\nec A \imp \nec \nec A $) and 5 ($\pos A \imp \nec \pos A$). From a semantic point of view, these axioms correspond to geometric frame conditions that must be satisfied by the accessibility relation in Kripke models (See for example \citep{fitting2} or \citep[Section 3.1]{blackburn} on Frame definability): T corresponds to reflexivity, B corresponds to symmetry, 4 corresponds to transitivity and 5 corresponds to euclidianity. In the models of logic {\bf S5}, all these axioms are satisfied; in the models of logic {\bf KB}, K and B are satisfied; and in the models of logic {\bf B}, K, T and B are satisfied.

@@

\bibitem[{\itshape Blackburn \& al.(2001)}]{blackburn}
Blackburn, P. \&  M. de Rijke \& Y. Venema. 2001. {\itshape Modal Logic}. Cambridge: Cambridge University Press.

@@

% @inproceedings{IJCAI2016,
%   author = {Benzm?ller, C. and Woltzenlogel Paleo, B.},
%   title  = {The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics},
%   booktitle = {International Joint Conference on Artificial Intelligence - IJCAI},
%   keywords ={HOML,Bruno,COREA*},
%   year = {2016}
% }

% @article{AndersonHajekControversy,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     journal = {Logica Universalis},
%     publisher = {Springer},
%     issn = {1661-8297},
%     volume = {10},
%     year = {2016},
%     keywords = {Bruno,HOML},
%     pages = {1--10},
%     note = {\emph{Accepted for publication on the 28th of February 2016}}
% }

% @inproceedings{WorldCongressLogicAndReligion,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     booktitle = {1st World Congress on Logic and Religion},
%     year = {2015},
%     keywords = {Bruno,Abstract,HOML},
%     pages = {49--50}
% }

% @inproceeding{WADT,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {Recent Trends in Algebraic Development Techniques},
%    year = {2014},
%    crossref = {ADT},
%    keywords = {Bruno,Invited,HOML},
%    note = {\textbf{[Invited]} }
% }

% @inproceedings{SpiritualQuest,
%   author    = {Christoph Benzm?ller and Bruno Woltzenlogel Paleo},
%   title     = {Experiments in Computational Metaphysics: G?del's Proof of God's Existence},
%   booktitle = {Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November)},
%   year      = {2015},
%   crossref  = {SpiritualQuest},
%   volume    = {9},
%   keywords  = {Bruno,Invited,HOML},
%   note = {\textbf{[Invited]} },
%   pages = {23--40}
% }

@@

% @inproceedings{SquareOfOpposition,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {Formalization and Automated Verification of G?del's Proof of God's Existence},
%    booktitle = {4th World Congress on the Square of Opposition},
%    year = {2014},
%    keywords = {Bruno,Abstract,HOML},
%    pages = {24--25}
% }

% @inworkshopinvited{WADTPreProceedings,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {22nd International Workshop on Algebraic Development Techniques},
%    year = {2014},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {8--9},
%    url = {http://wadt2014.cs.ovgu.de/pre-proceedings.pdf}
% }

% @article{ModalCollapse,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {The Modal Collapse as a Collapse of the Modal Square of Opposition},
%    journal = {Studies in Universal Logic},
%    publisher = {Springer},
%    issn = {2297-0282},
%    year = {2016},
%    keywords = {Bruno,HOML},
%    pages   =  {1--7},
%    note    = {\emph{Submitted in November 2014. Accepted for publication on the 28th of February 2016}}
% }

% @article{IsabelleGod,
%   author    = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%   title     = {G{\"{o}}del's God in Isabelle/HOL},
%   journal   = {Archive of Formal Proofs},
%   year      = {2013},
%   volume    = {},
%   keywords  = {Bruno,DBLP,HOML},
%   url       = {http://afp.sourceforge.net/entries/GoedelGod.shtml},
%   timestamp = {Wed, 15 Oct 2014 15:14:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/journals/afp/Benzmueller13},
%   bibsource = {dblp computer science bibliography, http://dblp.org}
% }

% @inworkshopinvited{IWIL,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {G?del's God on the Computer},
%    booktitle = {10th International Workshop on the Implementation of Logics},
%    year = {2013},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {1--2}
% }

% @article{AustrianComputerSociety,
%    author = {Woltzenlogel Paleo, Bruno},
%    title  = {Automated Verification and Reconstruction of G?del's Proof of God's Existence},
%    journal = {Journal of the Austrian Computer Society},
%    year = {2013},
%    keywords = {Bruno,Invited,S,HOML},
%    pages    = {4--6}
% }
